Challenges in Developing Great MCQMC Software

### 2022-07-17 MCQMC_2022_ChallengesDevelopSoftware.tex
Office Computer Updates

\usetheme{FJHSlimNoFoot169}
\setlength{\parskip}{2ex}
\setlength{\arraycolsep}{0.5ex}

@@

	\vspace{-5ex}
	\begin{itemize}
		\item \alert{Correct}, e.g., not omit the zeroth point in a low discrepancy sequence \parencite{Owe22a, scipySobol2020a}

@@

\begin{frame}{Why Do We Need Software?}
	\begin{itemize}
		\item \alert{Theory} 
		\begin{itemize}
			\item Explains and justifies \alert{algorithms}
			\item Assumptions$\implies$success should be viewed as failure$\implies$why
		\end{itemize}
		\item \alert{Software} 
		\begin{itemize}
			\item Makes \alert{algorithms} practical
			\item Solves (new) \alert{applications}
			\item Eliminates \alert{do-it-yourself}
		\end{itemize}
		\item \alert{Applications} 
  		\begin{itemize}
			\item Make \alert{societal} impact
			\item Inspire new \alert{theory}
		\end{itemize}

@@

	\item[Stopping Criterion] based on a data-driven error bound, whic determines how large $n$ should be to ensure that $\abs{\mu - \hmu_n} \le \varepsilon$
\end{description}

@@

    \item Diversity of multi-processor environments complicates software development; where does parallelism really help?

@@

\begin{frame}{Ex.\ Connecting QMCPy with FEniCS/Dolfin}
\vspace{-4ex}
	\begin{itemize}
		\item Want to demonstrate how our QMC software could work with a popular DE solver for DEs with random coefficients
		\item Partial success \only<3->{\alert{Why?}}
	\end{itemize}
 	\vspace{-2ex}
 \begin{minipage}{0.48\textwidth}
 	\only<1-2>{\begin{gather*}
 		-\frac{\dif }{\dif x}\biggl(a(x,\vW) \frac{\dif}{\dif x} u(x,\vW) \biggr) = 200( 2x - 1)\\
 		 0 \leq x \leq 1, \qquad
 		u(0) = u(1) = 0 \\
 		a(x,\vW) = 1 + 0.6 \sum_{k=1}^d \frac{W_k T_{k}(2x-1)}{k^2} \\
 		 \vW \sim \cu[-1,1]^d \\
 		 \Ex[u(0.25,\vW)] = \only<1>{\, ?}\only<2>{ -1.7462}
 	\end{gather*}}
  \only<3->{
\begin{itemize}
\item Even with FEniCS/Dolfin's extensive documentation we had \alert{difficulties}
\begin{itemize}
    \item Learning how to solve a simple ODE, so reverted to an older version
    \item Learning how to change the random instance of coefficient without tiggering the JIT compile
    \item Do not yet know how to express the random coefficient in terms of the covariance kernel
\end{itemize}
\end{itemize}
  }
 \end{minipage}%
\hfill
 \begin{minipage}{0.48\textwidth}
 	\only<1-2>{\centering
 	\includegraphics<1>[width=\textwidth]{ProgramsImages/axwtrue0.6.eps}
 	\includegraphics<2->[width=\textwidth]{ProgramsImages/timing-4.eps}}%
  \only<3->{
\begin{itemize}
\item But
\begin{itemize}
    \item It does work
    \item If we can overcome the challenges, will post a blog and demo at \textcite{QMCBlog}
\end{itemize}
\end{itemize}

@@

\section{Support}
\begin{frame}{Encouraging Users Requires}
	content...
\end{frame}

\begin{frame}{Connecting Demos}
	content...
\end{frame}

\begin{frame}{Building User \& Developer Ownership}
 Research Software Engineers International 	\url{https://researchsoftware.org}, ``Research Software Engineers are people who combine professional software expertise with an understanding of research. They go by various job titles but the term Research Software Engineer (RSE) is fast gaining international recognition.''
  \url{https://us-rse.org}
\end{frame}

\begin{frame}{From Private to Public}
	content...
\end{frame}

>>>>

\usetheme{FJHSlimNoFoot169}
\setlength{\parskip}{2ex}
\setlength{\arraycolsep}{0.5ex}
\setbeamersize{text margin top=10mm}

@@

	%\vspace{-5ex}
	\begin{itemize}
		\item \alert{Correct}, e.g., not omit the zeroth point in a low discrepancy sequence \parencite{Owe22a, scipySobol2020a}

@@

\begin{frame}{Why Do We Need Software?}
	\vspace{-5ex}
	\begin{itemize}
		\item \alert{Theory} 
		\begin{itemize}
			\item Explains and justifies \alert{algorithms}
			\item Assumptions$\implies$success should be viewed as failure$\implies$why
		\end{itemize}
		\item \alert{Software} 
		\begin{itemize}
			\item Makes \alert{algorithms} practical
			\item Solves (new) \alert{applications}
			\item Eliminates \alert{do-it-yourself}
		\end{itemize}
		\item \alert{Applications} 
  		\begin{itemize}
			\item Make \alert{societal} impact
			\item Inspire new \alert{theory}
		\end{itemize}

\uncover<2->{The United States Department of Energy is investing in studying how to develop great scientific software \parencite{Her19a,ASCR-SSSDU}}
\end{frame}

@@

	\item[Stopping Criterion] based on a data-driven error bound, which determines how large $n$ should be to ensure that $\abs{\mu - \hmu_n} \le \varepsilon$
\end{description}

@@

    \item Growth of multi-processor environments 
    \begin{itemize}
    	\item Provides opportunity
    	\item Complicates software development; where does parallelism really help?
    \end{itemize}

@@

\begin{frame}{Ex.\ Connecting QMCPy with FEniCS/Dolfin \parencite{}}
\vspace{-4ex}
	\begin{itemize}
		\item Want to demonstrate how our QMC software could work with a popular DE solver for DEs with random coefficients
		\item Partial success \only<3->{\alert{Why?}}
	\end{itemize}
 	\vspace{-2ex}
 \begin{minipage}{0.48\textwidth}
 	\only<1-2>{\begin{gather*}
 		-\frac{\dif }{\dif x}\biggl(a(x,\vW) \frac{\dif}{\dif x} u(x,\vW) \biggr) = 200( 2x - 1)\\
 		 0 \leq x \leq 1, \qquad
 		u(0) = u(1) = 0 \\
 		a(x,\vW) = 1 + 0.6 \sum_{k=1}^d \frac{W_k T_{k}(2x-1)}{k^2} \\
 		 \vW \sim \cu[-1,1]^d \\
 		 \Ex[u(0.25,\vW)] = \only<1>{\, ?}\only<2>{ -1.7462}
 	\end{gather*}}
  \only<3->{
\begin{itemize}
\item Even with FEniCS/Dolfin's extensive documentation we had \alert{difficulties}
\begin{itemize}
    \item Learning how to solve a simple ODE, so reverted to an older version
    \item Learning how to change the random instance of coefficient without tiggering the JIT compile
    \item Do not yet know how to express the random coefficient in terms of the covariance kernel
\end{itemize}
\end{itemize}
  }
 \end{minipage}%
\hfill
 \begin{minipage}{0.48\textwidth}
 	\only<1-2>{\centering
 	\includegraphics<1>[width=\textwidth]{ProgramsImages/axwtrue0.6.eps}
 	\includegraphics<2->[width=\textwidth]{ProgramsImages/timing-4.eps}}%
  \only<3->{
\begin{itemize}
\item But
\begin{itemize}
    \item It does work
    \item If we can overcome the challenges, will post a blog and demo at \textcite{QMCBlog}
\end{itemize}
\end{itemize}

@@

\section{Support}
\begin{frame}{Encouraging Users Requires}
	\begin{itemize}
		\item A repository where
		\begin{itemize}
		\item  Your library can be easily downloaded
		\item Issues or queries can be posted
		\item There are updates
		\end{itemize}
		\item (Elementary) \alert{demos} on how to use the software and highlighting  its advantages
		\item Demos \alert{connecting}  your library with others
		\item Recommending your students and postdocs to \alert{use} your library
		\item \alert{Welcoming} instructions on how to contribute an algorithm or a demo
	\end{itemize}

\begin{frame}{Building Developer Team}

\item Many senior researchers \alert{don't code}, and rely on transient team members (students, postdocs)
\begin{itemize}
	\item Encourage a sense of ownership that lasts beyond the time your team members are part of your lab
	\item Encourage 
\end{itemize}

\item Recognize good software as \alert{valuable} scholarly output

\item Recognize \alert{research software engineer} as a valued vocation; look at \alert{Research Software Engineers International} 	\url{https://researchsoftware.org}, \emph{Research Software Engineers are people who combine professional software expertise with an understanding of research. They go by various job titles but the term Research Software Engineer (RSE) is fast gaining international recognition.}
  \end{itemize}
\end{frame}
